Context-dependent consequences of including lagged effects in demographic models

### 2022-05-16 docs/paper.Rmd
add lifecycle diagram figure

-   Add figures

@@

Ultimately, we built and iterated three types of IPMs which each required different underlying vital rate model structure.
For all models, we used the long term demographic dataset for modeling survival, growth, and flowering.
For established plants, these three vital rates were modeled as a smooth function of size in the previous census using generalized additive models (GAMs) fit with the `mgcv` package[@mgcv] in `r version$version.string` [@rcoreteam2020].
Seedlings were considered a separate discrete class not structured by size.
For consistency, seedling survival and growth were also modeled using GAMs, but without size in the previous census as a predictor (i.e. intercept only models).
For growth models, a scaled t family distribution provided a better fit to the data than a gaussian fit as the residuals were leptokurtic with a simple gaussian model.

@@

# Draft of this figure is in docs/figures/Heliconia lifecycle DAG.key
```

Just playing with something here.
This is the population trajectories from the iterated IPMs with `normalize_pop_size=FALSE`.
I thought maybe I'd be able to see some (lagged) similarities between the kernel sampled and DLNM IPMs because they are run with the same sequence of years.
Nothing obvious pops out.
Not sure this figure is worth including.

>>>>

@@

Ultimately, we built and iterated three types of IPMs which each required different underlying vital rate model structure (Figure \@ref(fig:lifecycle)).
For all models, we used the long term demographic dataset for modeling survival, growth, and flowering.
For established plants, these three vital rates were modeled as a smooth function of size in the previous census using generalized additive models (GAMs) fit with the `mgcv` package[@mgcv] in `r version$version.string` [@rcoreteam2020].
Seedlings were considered a separate discrete class not structured by size.
For consistency, seedling survival and growth were also modeled using GAMs, but without size in the previous census as a predictor (i.e. intercept only models).
For growth models, a scaled t family distribution provided a better fit to the data than a gaussian fit as the residuals were leptokurtic with a simple gaussian model.

@@

# Draft of this figure is in docs/figures/Heliconia lifecycle DAG.key
knitr::include_graphics(here::here("docs", "figures", "lifecycle.png"))
```

Combine above figure with this table:

| Description                                  | Deterministic    | Stochastic, kernel-resampled | Stochastic, parameter-resampled (DLNM) |
|----------------------------------------------|------------------|------------------------------|----------------------------------------|
| Mature plant survival                        | $s(z)$           | $s_y(z)$                     | $s(z;\theta_{0-36})$                   |
| Seedling survival                            | $s_0$            | $s_{0_y}$                    | $s_0(\theta_{0-36})$                   |
| Mature plant growth or regression            | $G(z^\prime, z)$ | $G_y(z^\prime,z)$            | $G(z^\prime,z;\theta_{0-36})$          |
| Seedling growth into mature plant            | $G_0(z^\prime)$  | $G_{0_y}(z^\prime)$          | $G(z^\prime;\theta_{0-36})$            |
| Probability of flowering                     | $p_f(z)$         | $p_{f_y}(z)$                 | $p_f(z;\theta_{0-36})$                 |
| Size-specific fecundity                      | $f(z)$           | $f(z)$                       | $f(z)$                                 |
| Probability of germination and establishment | $g$              | $g$                          | $g$                                    |

<!--# probably can't make the figure with the table in it in R easily. -->\
\
Just playing with something here.
This is the population trajectories from the iterated IPMs with `normalize_pop_size=FALSE`.
I thought maybe I'd be able to see some (lagged) similarities between the kernel sampled and DLNM IPMs because they are run with the same sequence of years.
Nothing obvious pops out.
Not sure this figure is worth including.
